%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%

\begin{thebibliography}{8}
	\bibitem{ourpaper}
	Nakatsuka, Y., \& Ozturk, E. (2021, January). CACTI: Captcha avoidance via client-side TEE integration. In 30th USENIX Security Symposium (USENIX Security 21).



	\bibitem{ref1}
	Zhou, X., Xu, Z., Wang, C., \& Gao, M. (2022, June). PPMLAC: high performance chipset architecture for secure multi-party computation. In Proceedings of the 49th Annual International Symposium on Computer Architecture (pp. 87-101).

	\bibitem{ref2}
	Fass, Aurore, et al. "Doublex: Statically detecting vulnerable data flows in browser extensions at scale." Proceedings of the 2021 ACM SIGSAC Conference on Computer and Communications Security. 2021.

	\bibitem{sec1}
	Leavline, E. J., \& Singh, D. A. A. G. (2013). Hardware implementation of LZMA data compression algorithm. International Journal of Applied Information Systems (IJAIS), 5(4), 51-56.

	\bibitem{sec2}
	Alakuijala, J., Farruggia, A., Ferragina, P., Kliuchnikov, E., Obryk, R., Szabadka, Z., \& Vandevenne, L. (2018). Brotli: A general-purpose data compressor. ACM Transactions on Information Systems (TOIS), 37(1), 1-30.

	\bibitem{sec3}
	Chen, J., Daverveldt, M., \& Al-Ars, Z. (2021, June). FPGA Acceleration of Zstd Compression Algorithm. In 2021 IEEE International Parallel and Distributed Processing Symposium Workshops (IPDPSW) (pp. 188-191). IEEE.

	\bibitem{sec4}
	Bartík, M., Ubik, S., \& Kubalik, P. (2015, December). LZ4 compression algorithm on FPGA. In 2015 IEEE International Conference on Electronics, Circuits, and Systems (ICECS) (pp. 179-182). IEEE.

	\bibitem{sec5}
	Deutsch, P. (1996). Rfc1951: Deflate compressed data format specification version 1.3.

	\bibitem{url1}
	https://www.datasunrise.com/potential-db-threats/10-common-vulnerabilities/

	\bibitem{ref3}
	Williams, M. A., Dey, S., Barranco, R. C., Naim, S. M., Hossain, M. S., \& Akbar, M. (2018, December). Analyzing evolving trends of vulnerabilities in national vulnerability database. In 2018 IEEE International Conference on Big Data (Big Data) (pp. 3011-3020). IEEE.

\end{thebibliography}

